How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-01 tse-paper/content.tex
Lines
Done deduction

Techniques based on custom parsers (\#1
in \Cref{tab:litsur:techniques}) are inadquate for our comparison,
since their creation is manual and such a technique would not
generalize on the wide varitey of build logs we are interested in. The
closest we could come to the second entry, regular expression, is a
technique to automatically derive them: In particular, we implement a
technique based on
\emph{Program Synthesis by Example (PBE)}. This 
mimics regular expressions, the second most frequently occurring whose while simplifying
their development.

To work effectively with build logs, many humans anecdotally search
(``grep'') the logs for key phrases such as ``fail.'' Papers often
resorted to such a strategy when doing manual analysis (\#2
in \Cref{tab:litsur:techniques}), describing it with the word
``scan.'' Imitating this ad hoc approach of searching for specific
strings, we automatize it as \emph{Keyword Search (KWS)}.

>>>>

Techniques based on custom parsers (\#1
in \Cref{tab:litsur:techniques}) are inadquate for our comparison,
since their creation is manual and such a technique would not
generalize to the wide varitey of build logs we are interested in.
The
closest we could come to the second entry, regular expression, is a
technique to automatically derive them: in particular, we implement a
technique based on
\emph{Program Synthesis by Example (PBE)}.
This mimics regular expressions, while simplifying their development.

To work effectively with build logs, many humans anecdotally search
(``grep'') the logs for key phrases such as ``fail.'' Papers often
resorted to such a strategy when doing manual analysis (\#2
in \Cref{tab:litsur:techniques}), describing it with the word ``scan''
or other paraphrases. Imitating this ad hoc approach of searching for
specific strings, we automatize it as \emph{Keyword Search (KWS)}.
